%% Document-wide settings.
\documentclass[letterpaper]{article}
\title{timesheeting specification document}
\author{Thomas HOULLIER \href{mailto:pro@houllier.net}
         {\texttt{\textlangle pro@houllier.net\textrangle}}}

\usepackage[colorlinks=true, allcolors=blue,
            hyperfootnotes=false,
            pdfauthor={Thomas HOULLIER},
            pdftitle={timesheeting specification document}]
            {hyperref} % Links for ref/cite.

\input{preamble}

% Document
\begin{document}
\frenchspacing
\date{PRJ1-SPE1-v1.1 -- November 16, 2024}
\maketitle
\thispagestyle{FirstPage}

\begin{abstract}
  This is the specification document for the timesheeting project.
  It describes the requirements for a time management software for
  personal timesheets.
\end{abstract}

\begin{versionhistory}
  \vhEntry{1.0}{22JAN2024}{TH}{Creation}
  \vhEntry{1.1}{16NOV2024}{TH}
  {Reformulated the specification after the initial implementation draft.
    Modified the definitions.
    Modified reqs R-UHI-020, R-UHI-040, R-UHI-050, R-UEI-050, R-UGL-010,
    R-DES-040, R-ENI-030, R-ENI-040, R-HIS-010, R-LDC-060, R-ENV-010,
    R-LOG-040, R-QUA-010.
    Added reqs R-UHI-060, R-LDC-090, R-LDC-100, R-ACC-060, R-ACC-070,
    R-ACC-080, R-URE-020, R-LOG-025, R-QUA-025, R-QUA-050, R-REL-070.
    Removed reqs R-UEI-020, R-UEI-030, R-DES-025, R-STP-010, R-STP-020,
    R-STP-030, R-ENI-010, R-ENI-020, R-LDC-030, R-LDC-040, R-SAV-040,
    R-BAK-050, R-DEX-040, R-RWT-070, R-LOG-030, R-DOC-030, R-DOC-040.}
\end{versionhistory}
\setcounter{table}{0} % Reset the table counter.

\section*{Applicable documents}
{ \centering
\begin{tabularx}{\textwidth}{| c | X | c | c | X |} \hline
  Index & Title & Reference & Revision & Author \\ \hline
  AD1   & External timesheet format & PRJ1-IRS1 & v1.1 & Thomas HOULLIER \\
  \hline \end{tabularx} \par }

\section*{Document distribution}
The present document is distributed under the \emph{Creative Commons Attribution
4.0 International} license (\url{https://creativecommons.org/licenses/by/4.0/})
by its author Thomas HOULLIER.

Every document release is signed with the author's GPG key. A signature file
is provided along with the released document.

\tableofcontents
\printglossary[type=\acronymtype,style=index]
\pagestyle{plain}
\input{sections/introduction}
\input{sections/definitions}
\input{sections/requirements}

\appendix

%% \include{appendices}

\apptocmd{\thebibliography}{\raggedright}{}{}
\begingroup
\setstretch{0.6}
\setlength\bibitemsep{0pt}
\printbibliography
\endgroup
\end{document}
