%% Document-wide settings.
\documentclass[letterpaper]{article}
\title{External timesheet format}
\author{Thomas HOULLIER \href{mailto:pro@houllier.net}
         {\texttt{\textlangle pro@houllier.net\textrangle}}}

\usepackage[colorlinks=true, allcolors=blue,
            hyperfootnotes=false,
            pdfauthor={Thomas HOULLIER},
            pdftitle={External timesheet format}]
            {hyperref} % Links for ref/cite.

\input{preamble}

% Document
\begin{document}
\frenchspacing
\date{PRJ1-IRS1-v1.x -- XXX}
\maketitle
\thispagestyle{FirstPage}

\begin{abstract}
  This document describes the external timesheet format used by the
  timesheeting program to export timesheet data.
\end{abstract}

\begin{versionhistory}
  \vhEntry{1.0}{26OCT2024}{TH}{Creation}
  \vhEntry{1.1}{02NOV2024}{TH}
  {Added: IRS1-HED-075, IRS1-HED-085, IRS1-HED-150, IRS1-BDY-090, IRS1-BDY-100.
   Modified: IRS1-HED-150.
   Example file updated accordingly.}
 \vhEntry{1.2}{XXX}{TH}{
   Modified: IRS1-HED-080 changed fixed-size to variable-size string.
   Example file updated accordingly.}
\end{versionhistory}
\setcounter{table}{0} % Reset the table counter.

\section*{Reference documents}
{ \centering
  \begin{tabularx}{\textwidth}{| c | X | c | c | X |} \hline
    Index & Title & Reference & Revision & Author \\ \hline
    RD1 & timesheeting specification document & PRJ1-SPE1 & v1.0 & Thomas
    HOULLIER \\ \hline
    RD2 & List of tz database time zones &
    \cite{wiki:tz_list} & 1246415064 & Wikipedia \\ \hline
  \end{tabularx} \par }

\section*{Document distribution}
The present document is distributed under the \emph{Creative Commons Attribution
  4.0 International} license (\url{https://creativecommons.org/licenses/by/4.0/})
by its author Thomas HOULLIER.

Every document release is signed with the author's GPG key. A signature file
is provided along with the released document.

\tableofcontents
\printglossary[type=\acronymtype,style=index]
\pagestyle{plain}
\input{sections/introduction}
\input{sections/definitions}
\input{sections/requirements}
\input{sections/example}

\appendix

%% \include{appendices}

\apptocmd{\thebibliography}{\raggedright}{}{}
\begingroup
\setstretch{0.6}
\setlength\bibitemsep{0pt}
\printbibliography
\endgroup
\end{document}
