\section{Modules requirements}
\subsection{version}
The \emph{version} module configures the versions of program components,
to ensure compatibility between different executables and \gls{DB}.

\paragraph{MR-VER-010 -- Program version number}
The \emph{version} module shall provide a program version number
as a string in the following format: \lstinline{x.y},
with \lstinline{x} the major revision number and \lstinline{y} the
minor revision number. The major version number and minor version
number are both integers. Zero is an acceptable version number.

The program version number may be suffixed with \lstinline{dev} to
indicate an internal development version.

Valid program version number examples are:
\begin{itemize}
\item \lstinline{0.5}: for major version 0, minor version 5.
\item \lstinline{3.1}: for major version 3, minor version 1.
\item \lstinline{3.1dev}: for a development version after \lstinline{3.1}.
\end{itemize}

\textit{uplink: } R-REL-010 -- Software version format

\textit{Tested by: } MT-VER-010 Program version number.

\paragraph{MR-VER-020 -- DB version number}
The \emph{version} module shall provide a \gls{DB} version number as
a positive integer.

\textit{uplink: } TODO DB module.

\textit{Tested by: } MT-VER-020 DB version number.

\subsection{config}
The \emph{config} module loads the configuration file, translates the parameters
into an internal representation and transmits them to the rest of the program.

\subsubsection{Configuration file loading}

\paragraph{MR-CON-010 -- Load from path}
The \emph{config} module shall load any compliant user configuration file when
provided with its path.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-010 Config file loading.

\paragraph{MR-CON-020 -- Non-existent path}
The \emph{config} module shall emit an exception when the path provided for the
configuration file corresponds to a file which does not exist.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-020 Non-existent path.

\paragraph{MR-CON-030 -- Default configuration file locations}
The \emph{config} module shall provide a default load method which looks
for the configuration file \lstinline{timesheeting/timesheeting.toml}
in the following default locations, in order of preference,
\begin{enumerate}
  \item \lstinline{$XDG_CONFIG_HOME}
  \item \lstinline{$HOME/.config/}
  \item \lstinline{/etc/}
\end{enumerate}

\textit{uplink: } TODO.

\paragraph{MR-CON-040 -- Default configuration file not found}
The \emph{config} module default load method shall emit an exception if
no configuration file was found in any of the default locations.

\textit{uplink: } TODO.

\subsubsection{Logger configuration}
\paragraph{MR-CON-050 -- Log filepath}
The \emph{config} module shall load from the configuration file a filepath
for the log file. This parameter is at the node \lstinline{log.file}.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-030 Log filepath.

\paragraph{MR-CON-060 -- Log levels}
The \emph{config} module shall load from the configuration file a vector of
strings defining the active log levels. This parameter is at the node
\lstinline{log.active_levels}.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-040 Log levels.

\paragraph{MR-CON-065 -- Maximum log age}
The \emph{config} module shall load from the configuration file an
unsigned integer defining the maximum age of logs (for log rotation)
in seconds. This parameter is at the node \lstinline{log.max_log_age}.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-130 Maximum log age.

\subsubsection{DB configuration}
\paragraph{MR-CON-070 -- DB filepath}
The \emph{config} module shall load from the configuration file a filepath
for the DB file. This parameter is at the node \lstinline{db.file}.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-050 DB filepath.

\subsubsection{Timezone configuration}
\paragraph{MR-CON-080 -- Timezone string}
The \emph{config} module shall load from the configuration file a string
representing the timezone to use. This parameter is at the node
\lstinline{time.timezone}.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-060 Timezone string.

\subsubsection{Duration display configuration}
\paragraph{MR-CON-090 -- Duration display days}
The \emph{config} module shall load from the configuration file a float
representing the number of hours in a workday for duration display.
This parameter is at the node \lstinline{time.hours_per_workday}.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-070 Duration display days.

\subsubsection{Key bindings configuration}
The key bindings are loaded into maps from key to action. The maps are,
\begin{itemize}
\item The \emph{normal map}, which is the binding map for the normal mode,
\item The \emph{edit map}, which is the binding map for the edit mode.
\end{itemize}

The normal mode is the regular mode of operation of the program, entered
upon program launch. The edit mode is used when typing text.
For the purpose of organization of the user-facing configuration file,
the normal mode bindings are separated into the sections \lstinline{navigation}
and \lstinline{actions}, while the edit mode bindings are under the section
\lstinline{edit\_mode}.

\paragraph{MR-CON-100 -- Binding list}
The \emph{config} module shall load bindings from the following nodes,
organized hierarchically. The top level node is \lstinline{keys}.

The \emph{normal map} bindings are loaded from,
\begin{itemize}
\item navigation
  \begin{itemize}
  \item up
  \item down
  \item left
  \item right
  \item subtabs
  \item previous
  \item next
  \item duration\_display
  \item entries\_screen
  \item projects\_screen
  \item locations\_screen
  \item project\_report\_screen
  \item weekly\_report\_screen
  \item active\_visibility
  \item quit
  \end{itemize}
\item actions
  \begin{itemize}
  \item commit\_entry
  \item set\_now
  \item add
  \item rename
  \item remove
  \item active\_toggle
  \item task\_project\_change
  \end{itemize}
\end{itemize}

The \emph{edit map} bindings are loaded from,
\begin{itemize}
\item edit\_mode
  \begin{itemize}
  \item validate
  \item cancel
  \item select\_suggestion
  \end{itemize}
\end{itemize}

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-080 Bindings loading.

\paragraph{MR-CON-110 -- Regular keys}
The \emph{config} module shall allow binding any regular (\textit{ie}
non-escaped and non-special) character key to any binding action.
The regular keys are designated by their character in the configuration
file, \textit{ie} the key \lstinline{e} is designated by the character
\lstinline{"e"} in the configuration file.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-080 Bindings loading.

\paragraph{MR-CON-120 -- Special keys}
The \emph{config} module shall allow binding the following special
keys to any binding action. The special keys are designated by strings.
\begin{itemize}
\item \lstinline{ESCAPE}: the escape key.
\item \lstinline{ENTER}: the enter or \emph{return} key.
\item \lstinline{SPACE}: the spacebar.
\item \lstinline{TAB}: the tabulation key.
\item \lstinline{UP}: the up arrow key.
\item \lstinline{DOWN}: the down arrow key.
\item \lstinline{LEFT}: the left arrow key.
\item \lstinline{RIGHT}: the right arrow key.
\end{itemize}

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-080 Bindings loading.

\paragraph{MR-CON-130 -- Multiple keys for an action}
The \emph{config} module shall allow binding multiple keys to the
same action. The keys are specified as a list of strings attached
to the corresponding action node.

For instance, for binding the keys \lstinline{e} and \lstinline{a}
to the action with node \lstinline{rename}, the configuration file
line is: \lstinline{rename = ["e", "a"]}.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-080 Bindings loading.

\paragraph{MR-CON-140 -- Protection against duplicates}
The \emph{config} module shall emit an exception when the configuration
file contains duplicate keys bound in the same map (\textit{ie} either
\emph{normal} or \emph{edit}).

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-090 Binding duplicate.

\paragraph{MR-CON-150 -- Backspace mapping}
The \emph{config} module shall map the backspace key to a backspace
action in the \emph{edit} map. This is done outside of the configuration
file, it is an implicit binding.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-100 Backspace mapping.

\paragraph{MR-CON-160 -- Unbound keys}
The maps in the \emph{config} module shall return an \emph{unbound}
action when queried with a key which was not bound during configuration.

\textit{uplink: } TODO.

\textit{Tested by: } MT-CON-110 Unbound mappings.

\paragraph{MR-CON-170 -- Invalid key strings}
The \emph{config} module shall emit an exception when a key
string in the configuration file does not map to any regular or \emph{special}
characters.

\textit{Tested by: } MT-CON-120 Invalid special key.

\subsection{cli}
\paragraph{MR-CLI-010}
TODO: uplink

\subsection{core}
The \emph{core} module contains several objects used throughout the program.

\paragraph{MR-COR-010 -- Generic item}
The items Project, Task and Location shall all be represented as objects with
the following attributes,
\begin{enumerate}
\item id,
\item name,
\item active (boolean flag to indicate whether the item is active or not).
\end{enumerate}
TODO: uplink

\textit{Tested by: } MT-COR-010 Project generic item,
MT-COR-020 Task generic item, MT-COR-030 Location generic item.

\paragraph{MR-COR-020 -- Vector of generic item names}
A vector of generic items shall be convertible to a vector of their names,
in order.

\textit{Tested by: } MT-COR-040 Vector of generic item names.

\paragraph{MR-COR-030 -- Entry}
Entries shall be represented as objects with the following attributes,
\begin{enumerate}
\item id,
\item project name,
\item task name,
\item start date,
\item stop date,
\item location name.
\end{enumerate}

\textit{Tested by: } MT-COR-050 Entry object.

\paragraph{MR-COR-040 -- Entry to strings}
Entries shall be convertible to a vector of strings for display.
These strings are, in order,
\begin{enumerate}
\item project name,
\item task name,
\item start date display string (long format),
\item stop date display string (long format),
\item location name.
\end{enumerate}

\textit{Tested by: } MT-COR-060 Entry to strings.

\paragraph{MR-COR-050 -- Entry to short strings}
Entries shall be convertible to a vector of strings with the same composition
as in MR-COR-040, except the dates are outputted in short format.

\textit{Tested by: } MT-COR-070 Entry to short strings.

\paragraph{MR-COR-060 -- Entry staging}
The entry staging state shall be represented as an object with the following
attributes,
\begin{enumerate}
\item project name,
\item task name,
\item start date,
\item stop date,
\item location name.
\end{enumerate}

These attributes are optional, meaning they may hold a value or not.

\textit{Tested by: } MT-COR-080 Entry staging with values,
MT-COR-090 Entry staging without values.

\paragraph{MR-COR-070 -- Entry staging to strings}
The entry staging object shall be convertible to a vector of string
representations of its attributes, in order, with the dates in
long format. Attributes which do not hold values are converted to a
single whitespace character.

\textit{Tested by: } MT-COR-100 Entry staging with values to strings,
MT-COR-110 Entry staging without values to strings.

\paragraph{MR-COR-080 -- Entry staging to short strings}
The entry staging object shall be convertible to the same vector
of strings as specified in MR-COR-070 except with the dates in short
format.

\textit{Tested by: } MT-COR-120 Entry staging with values to short strings,
MT-COR-130 Entry staging without values to short strings.

\paragraph{MR-COR-090 -- Export row}
Export rows (for CSV file export) shall be represented as an object
with the following attributes,
\begin{enumerate}
\item entry id,
\item project id,
\item project name,
\item task id,
\item task name,
\item location id,
\item location name,
\item start date,
\item stop date.
\end{enumerate}

\textit{Tested by: } MT-COR-140 Export row.

\paragraph{MR-COR-100 -- Export csv string}
Export rows shall be convertible to a string representation with
comma-separated attributes. The dates are converted to unix timestamps.

\textit{Tested by: } MT-COR-150 Export row csv string.

\paragraph{MR-COR-110 -- Project total}
Project total (report of time worked per task) shall be represented
as objects with the following attributes,
\begin{enumerate}
\item project name,
\item total (Duration),
\item vector of task totals.
\end{enumerate}

Each task total has the following attributes,
\begin{enumerate}
\item task name,
\item total (Duration).
\end{enumerate}

\textit{Tested by: } MT-COR-160 Project total instantiation.

\paragraph{MR-COR-120 -- Project total to menu items}
Project total objects shall be convertible to menu items for the TUI,
indicating,
\begin{enumerate}
\item The string to display in the cell,
\item The string to display in the status bar,
\item The string face to use (bold, italics etc.).
\end{enumerate}

The menu items are ordered in a nested fashion, with tasks grouped per
project, and the overall project total displayed first in bold.
The menu items are in lexicographic order.

An example of menu items as displayed is shown in
\cref{tab:project_total_menu_items}.

\begin{table} \caption{\label{tab:project_total_menu_items} Menu items for
    project total.}
  \begin{tabular}{| c | c |} \hline
    \textbf{Project1} & \textbf{13.202 hours} \\ \hline
    Task1 & 1.202 hours \\ \hline
    Task2 & 3.000 hours \\ \hline
    Task3 & 9.000 hours \\ \hline
  \end{tabular}
\end{table}

\textit{Tested by: } MT-COR-170 Project total to menu items.

\paragraph{MR-COR-130 -- Weekly totals}
Weekly totals (report of time worked per task in a week) shall be represented
as objects with the following attributes,
\begin{enumerate}
\item total duration worked in the week,
\item total duration worked per day in the week,
\item vector of per project totals.
\end{enumerate}

Note a week has seven days and starts on monday.

Each per project total has the following attributes,
\begin{enumerate}
\item project name,
\item total duration worked on the project in the week,
\item total duration worked on the project per day,
\item vector of per task totals.
\end{enumerate}

Each per task total has the following attributes,
\begin{enumerate}
\item task name,
\item total duration worked on the task in the week,
\item total duration worked on the task per day.
\end{enumerate}

\textit{Tested by: } MT-COR-180 Weekly totals instantiation.

\paragraph{MR-COR-140 -- Weekly totals to menu items}
Weekly total objects shall be convertible to menu items for the TUI,
indicating,
\begin{enumerate}
\item The string to display in the cell,
\item The string to display in the status bar,
\item The string face to use (bold, italics etc.).
\end{enumerate}

The menu items are in lexicographic order. A column header
precedes the actual data. The menu items are, in order,
\begin{enumerate}
\item A header line indicating the columns
  \lstinline{Task, Mon, Tue, Wed, Thu, Fri, Sat, Sun, TOTAL} in normal face.
\item An all-tasks line, indicating the weekly total and daily breakdown of
  the total.
\item Per-project breakdown of weekly totals, with the project total first
  in bold face, following by all individual tasks in normal face.
\end{enumerate}

An example of menu items as displayed is shown in
\cref{tab:weekly_total_menu_items}.

\begin{table} \caption{\label{tab:weekly_total_menu_items} Menu items for
    weekly total.}
  \begin{tabular}{| c | c | c | c | c | c | c | c | c |} \hline
    Task & Mon & Tue & Wed & Thu & Fri & Sat & Sun & TOTAL \\ \hline
    ALL & 13.108 & 7.138 & 4.114 & 9.807
        & 12.498 & 12.386 & 12.039 & 71.090 \\ \hline
    \textbf{Project1} & \textbf{13.108} & \textbf{2.138} & \textbf{2.000}
                      & \textbf{4.807} & \textbf{6.000} & \textbf{7.386}
                      & \textbf{7.039} & \textbf{42.478} \\ \hline
    Task1 & 3.108 & 1.138 & 1.000
          & 2.807 & 3.000 & 2.386
          & 2.039 & 15.478 \\ \hline
    Task2 & 5.000 & 0.500 & 0.400
          & 0.500 & 2.000 & 2.500
          & 3.000 & 13.900 \\ \hline
    Task3 & 5.000 & 0.500 & 0.600
          & 1.500 & 1.000 & 2.500
          & 2.000 & 13.100 \\ \hline
    \textbf{Project2} & & \textbf{5.000} & \textbf{2.114}
                      & \textbf{5.000} & \textbf{6.498} & \textbf{5.000}
                      & \textbf{5.000} & \textbf{28.612} \\ \hline
    Task4 & & 5.000 & 2.114
          & 5.000 & 6.498 & 5.000
          & 5.000 & 28.612 \\ \hline
  \end{tabular}
\end{table}

\textit{Tested by: } MT-COR-190 Weekly totals to menu items.

\subsection{db}
The DB module contains a singleton which interacts with the \gls{DB}.
It is the unique point of direct interaction with the DB in the program,
either in read or write.

\paragraph{MR-DBI-010 -- DB loading}
The DB object shall be loaded using a filepath to the \gls{DB} file.
TODO: uplink

\textit{Tested by: } MT-DBI-010 DB singleton grab.

\paragraph{MR-DBI-020 -- DB get user version}
The DB object shall allow retrieving the user version number of the
loaded DB.

\textit{Tested by: } MT-DBI-020 DB get user version.

\subsubsection{DB tables}
\paragraph{MR-DBI-030 -- Projects table}
The \gls{DB} shall contain a \emph{projects} table with the following columns,
\begin{enumerate}
\item id,
\item name,
\item active (boolean flag).
\end{enumerate}

\paragraph{MR-DBI-040 -- Unique project names}
The \emph{projects} table shall only allow unique names.

\textit{Tested by: } MT-DBI-060 Unique project names,
MT-DBI-260 Project name edit unique.

\paragraph{MR-DBI-050 -- Tasks table}
The \gls{DB} shall contain a \emph{tasks} table with the following columns,
\begin{enumerate}
\item id,
\item name,
\item project\textunderscore id (id from the \emph{projects} table),
\item active (boolean flag).
\end{enumerate}

\paragraph{MR-DBI-060 -- Unique task names per project}
The \emph{tasks} table shall only allow unique names per project.
Two tasks are allowed to have the same name if they are in different
projects.

\textit{Tested by: } MT-DBI-080 Unique task names,
MT-DBI-300 Task name edit unique,
MT-DBI-320 Task project edit unique.

\paragraph{MR-DBI-070 -- Project's tasks deletion}
Upon deletion of a project, all its corresponding tasks must also
be deleted.
Note deletion is only possible if no task in the project is present
in entries.

\textit{Tested by: } MT-DBI-090 Project's tasks deletion.

\paragraph{MR-DBI-080 -- Locations table}
The \gls{DB} shall contain a \emph{locations} table with the following columns,
\begin{enumerate}
\item id,
\item name,
\item active (boolean flag).
\end{enumerate}

\paragraph{MR-DBI-090 -- Unique location names}
The \emph{locations} table shall only allow unique names.

\textit{Tested by: } MT-DBI-070 Unique location names,
MT-DBI-280 Location name edit unique.

\paragraph{MR-DBI-100 -- Entries table}
The \gls{DB} shall contain an \emph{entries} table with the following columns,
\begin{enumerate}
\item id,
\item task\textunderscore id (id from the \emph{tasks} table),
\item start (start date UTC UNIX timestamp),
\item stop (stop date UTC UNIX timestamp),
\item location\textunderscore id (id from the \emph{locations} table).
\end{enumerate}

\paragraph{MR-DBI-110 -- Entries locking hierarchy items removal}
The \emph{locations} and \emph{tasks} referenced to in \emph{entries} shall be
locked for removal, along with their corresponding project. \emph{Locations},
\emph{tasks} and \emph{projects} may only be removed once no part of
\emph{entries} references them.

\textit{Tested by: } MT-DBI-790 Locked project removal,
MT-DBI-800 Locked task removal,
MT-DBI-810 Locked location removal.

\paragraph{MR-DBI-120 -- Entries start stop ordering}
The \emph{entries} table shall only allow \emph{start} and \emph{stop}
values for which $start < stop$.

\textit{Tested by: } MT-DBI-520 Committing wrong date order,
MT-DBI-530 Committing zero duration entry.

\paragraph{MR-DBI-130 -- Entries non-overlapping dates}
The \emph{entries} table shall only allow items with non-overlapping
\emph{start} and \emph{stop} dates.

\textit{Tested by: } MT-DBI-570 Overlapping entry with stop,
MT-DBI-580 Overlapping entry with start,
MT-DBI-590 Overlapping entry, both dates inside,
MT-DBI-600 Overlapping entry, both dates on either side.

\paragraph{MR-DBI-140 -- Entry staging table}
The \gls{DB} shall contain an \emph{entrystaging} table with the following
columns,
\begin{enumerate}
\item task\textunderscore id (id from the \emph{tasks} table),
\item start,
\item stop,
\item location\textunderscore id (id from the \emph{locations} table).
\end{enumerate}

Note the \emph{entrystaging} table only ever has one row.

\subsubsection{Hierarchy items}
\paragraph{MR-DBI-150 -- Inserting projects}
The \gls{DB} shall allow inserting new \emph{projects}, identified by a name
string. The operation must return true for success and false in case
a constraint was violated.

\textit{Tested by: } MT-DBI-030 Projects addition, querying and deletion.

\paragraph{MR-DBI-160 -- Projects active default}
The newly inserted projects shall be active by default.

\textit{Tested by: } MT-DBI-100 Projects active default.

\paragraph{MR-DBI-170 -- Inserting tasks}
The \gls{DB} shall allow inserting new \emph{tasks}, identified by the parent
project id, and a name string. The operation must return true for success
and false in case a constraint was violated.

\textit{Tested by: } MT-DBI-050 Tasks addition, querying and deletion.

\paragraph{MR-DBI-180 -- Tasks active default}
The newly inserted tasks shall be active by default.

\textit{Tested by: } MT-DBI-120 Tasks active default.

\paragraph{MR-DBI-190 -- Inserting locations}
The \gls{DB} shall allow inserting new \emph{locations}, identified by a name
string. The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-040 Locations addition, querying and deletion.

\paragraph{MR-DBI-200 -- Locations active default}
The newly inserted locations shall be active by default.

\textit{Tested by: } MT-DBI-110 Locations active default.

\paragraph{MR-DBI-210 -- Project name edit}
The \gls{DB} shall allow editing the name of existing \emph{projects}.
The projects are identified by their id. The operation must return true for
success and false in case a constraint was violated.

\textit{Tested by: } MT-DBI-250 Project name edit,
MT-DBI-260 Project name edit unique.

\paragraph{MR-DBI-220 -- Task name edit}
The \gls{DB} shall allow editing the name of existing \emph{tasks}.
The tasks are identified by their id. The operation must return true for success
and false in case a constraint was violated.

\textit{Tested by: } MT-DBI-290 Task name edit,
MT-DBI-300 Task name edit unique.

\paragraph{MR-DBI-230 -- Task project edit}
The \gls{DB} shall allow editing the project id of existing \emph{tasks}.
The tasks are identified by their id, and projects by their name.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-310 Task project edit,
MT-DBI-320 Task project edit unique,
MT-DBI-330 Task project edit nonexistent.

\paragraph{MR-DBI-240 -- Location name edit}
The \gls{DB} shall allow editing the name of existing \emph{locations}.
The locations are identified by their id.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-270 Location name edit,
MT-DBI-280 Location name edit unique.

\paragraph{MR-DBI-250 -- Toggle project active}
The \gls{DB} shall allow toggling the active status of existing \emph{projects}.
The projects are identified by their id.

\textit{Tested by: } MT-DBI-160 Toggle project active.

\paragraph{MR-DBI-260 -- Toggle task active}
The \gls{DB} shall allow toggling the active status of existing \emph{tasks}.
The tasks are identified by their id.

\textit{Tested by: } MT-DBI-180 Toggle task active.

\paragraph{MR-DBI-270 -- Toggle location active}
The \gls{DB} shall allow toggling the active status of existing \emph{locations}.
The locations are identified by their id.

\textit{Tested by: } MT-DBI-170 Toggle location active.

\paragraph{MR-DBI-280 -- Query projects}
The \gls{DB} shall allow querying the list of existing \emph{projects}.
The result is in alphabetical order.

\textit{Tested by: } MT-DBI-030 Projects addition, querying and deletion,
MT-DBI-130 Query projects ordering.

\paragraph{MR-DBI-290 -- Query active projects}
The \gls{DB} shall allow querying the list of active \emph{projects}.
The result is in alphabetical order.

\textit{Tested by: } MT-DBI-190 Query active projects,
MT-DBI-220 Query active projects ordering.

\paragraph{MR-DBI-300 -- Query tasks of project}
The \gls{DB} shall allow querying the list of existing \emph{tasks}
for a given project id.
The result is in alphabetical order.

\textit{Tested by: } MT-DBI-050 Tasks addition, querying and deletion,
MT-DBI-150 Query tasks ordering.

\paragraph{MR-DBI-310 -- Query active tasks of project}
The \gls{DB} shall allow querying the list of active \emph{tasks}
for a given project id.
The result is in alphabetical order.

\textit{Tested by: } MT-DBI-210 Query active tasks,
MT-DBI-240 Query active tasks ordering.

\paragraph{MR-DBI-320 -- Query locations}
The \gls{DB} shall allow querying the list of existing \emph{locations}.
The result is in alphabetical order.

\textit{Tested by: } MT-DBI-040 Locations addition, querying and deletion,
MT-DBI-140 Query locations ordering.

\paragraph{MR-DBI-330 -- Query active locations}
The \gls{DB} shall allow querying the list of active \emph{locations}.
The result is in alphabetical order.

\textit{Tested by: } MT-DBI-200 Query active locations,
MT-DBI-230 Query active locations ordering.

\paragraph{MR-DBI-340 -- Delete projects}
The \gls{DB} shall allow the deletion of existing \emph{projects},
identified by their id.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-030 Projects addition, querying and deletion.

\paragraph{MR-DBI-350 -- Delete tasks}
The \gls{DB} shall allow the deletion of existing \emph{tasks},
identified by their id.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-050 Tasks addition, querying and deletion.

\paragraph{MR-DBI-360 -- Delete locations}
The \gls{DB} shall allow the deletion of existing \emph{locations},
identified by their id.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-040 Locations addition, querying and deletion.

\subsubsection{Entry staging}
\paragraph{MR-DBI-370 -- Entry staging project name}
The \gls{DB} shall allow editing the \emph{entrystaging} project name.
Only active projects may be set.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-360 Entry staging project name,
MT-DBI-370 Entry staging task auto-fill,
MT-DBI-380 Entry staging non-existent project name,
MT-DBI-390 Entry staging active projects,
MT-DBI-510 Entry staging set project which has no tasks.

\paragraph{MR-DBI-380 -- Entry staging task name}
The \gls{DB} shall allow editing the \emph{entrystaging} task name.
Only active tasks may be set.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-400 Entry staging task name without project,
MT-DBI-410 Entry staging task name,
MT-DBI-420 Entry staging task name active,
MT-DBI-430 Entry staging task name non-existent.

\paragraph{MR-DBI-390 -- Entry staging start}
The \gls{DB} shall allow editing the \emph{entrystaging} start \emph{date}.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-470 Entry staging start date.

\paragraph{MR-DBI-400 -- Entry staging stop}
The \gls{DB} shall allow editing the \emph{entrystaping} stop \emph{date}.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-480 Entry staging stop date.

\paragraph{MR-DBI-410 -- Entry staging location}
The \gls{DB} shall allow editing the \emph{entrystaging} location name.
Only active locations may be set.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-440 Entry staging location name,
MT-DBI-450 Entry staging location name active,
MT-DBI-460 Entry staging location name non-existent.

\paragraph{MR-DBI-420 -- Entry staging commit}
The \gls{DB} shall allow committing the \emph{entrystaging} to an
\emph{entries} item.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-540 Committing missing task,
MT-DBI-550 Committing missing location,
MT-DBI-560 Committing valid entry,
MT-DBI-610 Valid second entry immediately following.

\paragraph{MR-DBI-430 -- Entry staging query}
The \gls{DB} shall allow the retrieval of the current \emph{entrystaging} item.

\textit{Tested by: } MT-DBI-340 Entry staging empty at first.

\paragraph{MR-DBI-440 -- Entry staging project id}
The \gls{DB} shall allow the retrieval of the current \emph{entrystaging}
project id. The return value is optional, as there is no value to
return in the case where no project/task is set in the entry staging.

\textit{Tested by: } MT-DBI-490 Entry staging project id,
MT-DBI-500 Entry staging project id no project.

\subsubsection{Entries}
\paragraph{MR-DBI-450 -- Entry project edit}
The \gls{DB} shall allow the editing of existing \emph{entries} project
by name.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-660 Entry project edit,
MT-DBI-665 Entry project edit auto-fill,
MT-DBI-670 Entry project edit no tasks,
MT-DBI-680 Entry project edit non-existent.

\paragraph{MR-DBI-460 -- Entry task edit}
The \gls{DB} shall allow the editing of existing \emph{entries} task
by name.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-690 Entry task edit,
MT-DBI-700 Entry task edit non-existent.

\paragraph{MR-DBI-470 -- Entry start edit}
The \gls{DB} shall allow the editing of existing \emph{entries} start
\emph{date}.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-730 Entry start edit,
MT-DBI-740 Entry start edit, wrong order,
MT-DBI-750 Entry start edit, overlapping.

\paragraph{MR-DBI-480 -- Entry stop edit}
The \gls{DB} shall allow the editing of existing \emph{entries} stop
\emph{date}.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-760 Entry stop edit,
MT-DBI-770 Entry stop edit, wrong order,
MT-DBI-780 Entry stop edit, overlapping.

\paragraph{MR-DBI-490 -- Entry location edit}
The \gls{DB} shall allow the editing of existing \emph{entries} location
by name.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-710 Entry location edit,
MT-DBI-720 Entry location edit non-existent.

\paragraph{MR-DBI-500 -- Entries query}
The \gls{DB} shall allow the retrieval of the list of existing \emph{entries}
in a given \emph{date range}. The entries shall be returned in
increasing order of start date.

\textit{Tested by: } MT-DBI-350 Entries empty at first,
MT-DBI-645 Entries query ordering.

\paragraph{MR-DBI-510 -- Entry project id query}
The \gls{DB} shall allow the retrieval of the project id associated to
a given item in \emph{entries}, identified by id.

\textit{Tested by: } MT-DBI-620 Entry project id query.

\paragraph{MR-DBI-520 -- Delete entry}
The \gls{DB} shall allow the deletion of existing \emph{entries}, by id.
The operation must return true for success and false in case a
constraint was violated.

\textit{Tested by: } MT-DBI-650 Delete entry.

\paragraph{MR-DBI-530 -- Entries duration over date range}
The \gls{DB} shall allow the retrieval of the total \emph{duration} worked
on \emph{entries} in a given \emph{date range}.

\textit{Tested by: } MT-DBI-630 Entries duration over date range,
MT-DBI-640 Entries duration over date range, zero duration.

\subsubsection{Reports}
\paragraph{MR-DBI-540 -- Entries export}
The \gls{DB} shall allow the export of entries to \emph{export row} format,
over a given \emph{date range}. The exported rows must be ordered by
increasing entry start date.

\textit{Tested by: } MT-DBI-820 Entries export,
MT-DBI-825 Entries export ordering,
MT-DBI-830 Entries export, empty.

\paragraph{MR-DBI-550 -- Project total}
The \gls{DB} shall allow the generation of a \emph{project total} report
over a given \emph{date range}. The projects must be ordered alphabetically,
and the same is required for the set of tasks inside each project.

\textit{Tested by: } MT-DBI-840 Project total report,
MT-DBI-850 Project total report, empty.

\paragraph{MR-DBI-560 -- Weekly totals}
The \gls{DB} shall allow the generation of a \emph{weekly totals} report
over a given \emph{week}.

\textit{Tested by: } MT-DBI-860 Weekly totals report,
MT-DBI-870 Weekly totals report, empty.

\subsection{keys}
\paragraph{MR-KEY-010}
TODO: uplink

\subsection{tui}
\paragraph{MR-TUI-010}
TODO: uplink

\subsection{exporter}
\paragraph{MR-EXP-010 -- Export file}
The exporter module shall produce an export file compliant with [AD7],
given a set of entry \emph{export rows} in a given \emph{date range},
and the filepath to the target export file.

\textit{Tested by: } MT-EXP-050 Export file.

\paragraph{MR-EXP-020 -- Export file directory exception}
If a directory is provided to the exporter module instead of a filepath,
then an exception shall be thrown.

\textit{Tested by: } MT-EXP-010 Export file directory exception.

\paragraph{MR-EXP-030 -- Export file exists exception}
If the filepath provided to the exporter module corresponds to
a file which already exists, then an exception shall be thrown.

\textit{Tested by: } MT-EXP-020 Export file exists exception.

\paragraph{MR-EXP-040 -- Export file non-existent path exception}
If the filepath provided to the exporter module corresponds
to a non-existent parent directory, then an exception shall be thrown.

\textit{Tested by: } MT-EXP-030 Export file nonexistent path exception.
